Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-08-03 paper/current/main.tex
edits through si figs

%
% Figure - Global Network Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
	\caption{
		\textbf{Visualization of global mobility network.}
		The network demonstrates country-level structure, but not at the detail or the extent of the global UMAP projection (Fig.~\ref{fig:projection}a).
		Each node corresponds to an organization, whereas  weighted edges (not shown) correspond to the flow of mobile researchers between the two organization.
		Nodes are colored by the country of the organization.
		Nodes are positioned using the force atlas layout algorithm.
	}
	\label{fig:supp:network_vis}
\end{figure}

@@

%
% Figure - Pennsylvania Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Pennsylvania.pdf}
	\caption{
		\textbf{UMAP Projection of organizations in Pennsylvania.}
		UMAP projection of the embedding space of organizations in Pennsylvania reveal clustering based on geography, sector, and academic prestige.
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
		Color indicates the sector.
	}
	\label{fig:supp:proj_pennsylvania}
\end{figure}

@@

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
	\caption{
		\textbf{SemRank hierarchy is robust.}
		\textbf{a.} Spearman's $rho$ (n = 143) between Times prestige rank and embedding rank derived using SemAxis, with poles defined using the top and bottom (geographically matched) ranked universities.
		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles.
		Including more universities improves performance, but quickly saturates after around five universities.
		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by the number of universities used to define the poles (n).
		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
		The grey box corresponds to the top 20 and bottom 20 ranks.
	  	Spearman's $\rho$ details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis.
	}
	\label{fig:supp:semaxis_compare}
\end{figure}

%
% Figure - Network Centrality vs. Times
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/centrality_times_compare.pdf}
	\caption{
		\textbf{Network centrality is strongly correlated with Times ranking.}
		Comparison between the ranking of organizations by their network-centrality rank and their rank in the 2018 Times Higher Education ranking of U.S. Universities .
		The Times rank is correlated with degree centrality rank (\textbf{a}) with a Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with a Spearman's $\rho = 0.76$.
	}
	\label{fig:supp:centrality_times_compare}
\end{figure}

%
% Figure - Network Centrality vs. SemAxis
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_network_compare.pdf}
	\caption{
		\textbf{Network centrality less correlated with Embedding rank.}
		Comparison between the ranking of organizations by their network-centrality rank and the embedding rank derived with SemAxis with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities .
		Embedding rank is correlated with degree centrality rank (\textbf{a}) with a Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with a Spearman's $\rho = 0.55$.
	}
	\label{fig:supp:centrality_semaxis_compare}
\end{figure}

>>>>

%
% Figure - Global Network Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/co_occur_with_label.pdf}
	\caption{
		\textbf{Visualization of global mobility network.}
		The network demonstrates country-level structure, but not at the detail or the extent of the global UMAP projection (Fig.~\ref{fig:projection}a).
		Each node corresponds to an organization, whereas  weighted edges (not shown) correspond to the flow of mobile researchers between the two organization.
		Nodes are colored by the country of the organization.
		Nodes are positioned using the Force Atlas layout algorithm.
	}
	\label{fig:supp:network_vis}
\end{figure}

@@

%
% Figure - Pennsylvania Projection
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/umap_coordinate_region_Pennsylvania.pdf}
	\caption{
		\textbf{UMAP Projection of organizations in Pennsylvania.}
		UMAP projection of the embedding space of organizations in Pennsylvania reveals clustering based on geography, sector, and academic prestige.
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019.
		Color indicates the sector.
	}
	\label{fig:supp:proj_pennsylvania}
\end{figure}

@@

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
	\caption{
		\textbf{SemRank hierarchy is robust.}
		\textbf{a.} Spearman's $\rho$ ($n = 143$) between Times prestige rank and embedding rank derived using SemAxis, with poles defined using the top and bottom (geographically matched) ranked universities.
		Black points show spearman correlation using all organizations; white points show correlation using only universalizes not aggregated in the poles.
		Including more universities improves performance, but quickly saturates after around five universities.
		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by the number of universities used to define the poles (n).
		White points are those top and bottom 20 universities aggregated to define the ends of the axis.
		The grey box corresponds to the top 20 and bottom 20 ranks.
	  	Spearman's $\rho$ details the estimate from Spearman correlation between the two rankings using all universities, including those used to define the ends of each axis.
	}
	\label{fig:supp:semaxis_compare}
\end{figure}

%
% Figure - Network Centrality vs. Times
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/centrality_times_compare.pdf}
	\caption{
		\textbf{Network centrality is strongly correlated with Times ranking.}
		Comparison between the ranking of organizations by their network-centrality rank and their rank in the 2018 Times Higher Education ranking of U.S. Universities .
		The Times rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.73$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.76$.
	}
	\label{fig:supp:centrality_times_compare}
\end{figure}

%
% Figure - Network Centrality vs. SemAxis
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_network_compare.pdf}
	\caption{
		\textbf{Network centrality less correlated with Embedding rank.}
		Comparison between the ranking of organizations by their network-centrality rank and the embedding rank derived with SemAxis with poles defined using the top five to geographically-matched bottom five universities ranked by the 2018 Times Higher Education ranking of U.S. Universities .
		Embedding rank is correlated with degree centrality rank (\textbf{a}) with Spearman's $\rho = 0.45$, and is correlated with the eigenvector centrality rank (\textbf{b}) with Spearman's $\rho = 0.55$.
	}
	\label{fig:supp:centrality_semaxis_compare}
\end{figure}
